Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
edits to 2.0

We apply \system to four domains:
 building Boolean circuits; symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing problems; and Lisp-style functions on lists.
 For each of these we deliberately provide an impoverished
 set of programming primitives,
 and show that our algorithm discovers
 its own domain-specific vocabulary for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
 \begin{table}[b]
    \begin{tabular}{ll}
   \toprule
   Domain&Part of the learned DSL\\\midrule
   Circuits&\code{(nand (nand a a) (nand b b))}\\
   &\hspace{0.5cm} \emph{(an OR gate)}\\
   Regression& \code{(+ (* real x) real)} \\
      &\hspace{0.5cm} \emph{(a linear function of x)}\\
   Strings& \code{(join '' (split c s))}\\
   &\hspace{0.5cm} \emph{(delete occurrences of c in string s)}\\
   Lists& \code{(map (lambda (x) (+ x a)) l)}\\
   &\hspace{0.5cm} \emph{(add a to every element of list l)}
   \\\bottomrule
    \end{tabular}
    \caption{ Examples of structure found in DSLs  learned by our algorithm. \system builds a new DSL by discovering and reusing useful subroutines.}\label{initialExampleDSL}
 \end{table}

@@

Our goal  is to induce a DSL while finding programs solving each of the tasks.
Our strategy is to iterate through three steps: (1) searching for programs; (2) learning a neural recognition model -- which we use
to accelerate the search over programs -- and (3) improving the DSL.
The key observation is that these steps bootstrap off each other (Fig.~\ref{feeding}):
\\\noindent \textbf{Wake: Searching for programs.}  Our program search  is informed by both the DSL and the recognition model.
When these improve we find better programs.
\\\noindent\textbf{Sleep-R: Learning a recognition model.} The recognition model is trained both on samples from the DSL and on programs found by the search procedure. As the DSL improves and as search finds more programs, the recognition model gets both more data to train on and better data.
\\\noindent\textbf{Sleep-G: Improving the DSL.} We induce a DSL from the programs we have found so far which solve the tasks;
  as we solve more tasks, we can hone in on richer DSLs that more closely match the domain.

@@

Sec.~\ref{mathematicalFraming} frames this 3-step procedure as
a means of maximizing a lower bound on the posterior probability of the DSL given the tasks.
Sec.~\ref{explorationSection} explains how we search for programs that solve the tasks;
Sec.~\ref{recognitionSection} how we train a neural network to accelerate the search over programs; and
Sec.~\ref{grammarInductionSection}  how \system induces a DSL from programs.

>>>>

We apply \system to four domains:
 building Boolean circuits; symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing problems; and Lisp-style functions on lists.
 For each of these we deliberately provide an impoverished
 set of programming primitives,
 and show that our algorithm discovers
 its own domain-specific vocabulary for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
 \begin{table}[b]
    \begin{tabular}{ll}
   \toprule
   Domain&Part of the learned DSL\\\midrule
   Circuits&\code{(nand (nand a a) (nand b b))}\\
   &\hspace{0.5cm} \emph{(an OR gate)}\\
   Regression& \code{(+ (* real x) real)} \\
      &\hspace{0.5cm} \emph{(a linear function of x)}\\
   Strings& \code{(join '' (split c s))}\\
   &\hspace{0.5cm} \emph{(delete occurrences of c in string s)}\\
   Lists& \code{(map (lambda (x) (+ x k)) l)}\\
   &\hspace{0.5cm} \emph{(add k to every element of list l)}
   \\\bottomrule
    \end{tabular}
    \caption{ Examples of structure found in DSLs  learned by our algorithm. \system builds a new DSL by discovering and reusing useful subroutines.}\label{initialExampleDSL}
 \end{table}

@@

Our goal  is to induce a DSL while finding programs solving each of the tasks.
Our strategy is to iterate through three steps: (1) searching for programs; (2) learning a neural recognition model -- which we use
to accelerate the search over programs -- and (3) improving the DSL.
The key observation is that these steps bootstrap off each other (Fig.~\ref{feeding}):
\\\noindent \textbf{Wake: Searching for programs.}  Our program search  is informed by both the DSL and the recognition model.
  When these improve, we find better programs.
\\\noindent\textbf{Sleep-R: Learning a recognition model.} The recognition model is trained both on samples from the DSL and on programs found by the search procedure. As the DSL improves and as search finds more programs, the recognition model gets both more data to train on and better data.
\\\noindent\textbf{Sleep-G: Improving the DSL.} We induce a DSL from the programs we found which solve the tasks.
  As we solve more tasks, we can hone in on richer DSLs that more closely match the domain.

@@

Sec.~\ref{mathematicalFraming} frames this 3-step procedure as
a means of maximizing a lower bound on the posterior probability of the DSL given the tasks.
Sec.~\ref{explorationSection} explains how we search for programs that solve tasks;
Sec.~\ref{recognitionSection} explains how we train a neural network to accelerate program search; and
Sec.~\ref{grammarInductionSection} explains how we induce a DSL from programs.
